Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-11-07 main.tex
:art: Revise manuscript

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency by provide a passive beamforming gain. This paper investigates an IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS. Considering the rectifier nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user. Stationary solutions are achieved based on Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by Geometric Programming (GP) technique. It is confirmed that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH), such that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR). Simulation results also show that the introduction of IRS significantly enlarges the R-E region while preserving the waveform preference and transceiving strategy. Although the AP-IRS-user extra link is relatively weak, we found that the information and power benefits of passive beamforming scale much faster than those of active beamforming. It suggests using more active antennas for small-scale SWIPT and more passive elements for large-scale SWIPT. % The proposed design enables a joint control of transmitter, receiver and wireless channel.
	\end{abstract}

@@

			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the rectifier input power level and input waveform shape. It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then designed joint waveform and beamforming design for WPT. Simulation and experiments demonstrated that ignoring the energy harvester nonlinearity is inaccurate and emphasized the benefit of modeling such nonlinearity in real system design \cite{Kim2019,Kim2020a}. Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand the operation range. Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}. Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of PS and TS is in general the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?". This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g. modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
		\end{subsection}

@@

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Wu2019}. Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting. In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each reflector with the others switched off. To reduce estimation overhead and design complexity, \cite{Yang2019} exploited the spatial correlation and proposed a group-based IRS model where adjacent elements share a common reflection coefficient. Recent research also explored the possibility of integrating IRS into Orthogonal Frequency-Division Multiplexing (OFDM) systems. For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, to enable flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

		\begin{subsection}{IRS-Aided SWIPT}
			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT. It was argued in \cite{Wu2020b} that dedicated energy beam is power-inefficient and may cause interference, thus not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system. On the other hand, \cite{Tang2019} suggested that if the interference can be cancelled, multiple energy beams are generally required for the max-min harvested power problem. \cite{Wu2020a} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated. In such cases, a single energy stream is enough for all energy receivers. However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission and on an inaccurate and oversimplified linear energy harvester model.

			In this paper, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS. The contribution of the paper are listed as follows.

			\textit{First}, we introduce a novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design. This architecture can be seen to IRS-aided SWIPT what \cite{Clerckx2018b} is to SWIPT. Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user. A multi-carrier unmodulated power waveform (deterministic multisine) is superposed to a multi-carrier modulated information waveform to boost the energy transfer efficiency. The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS, and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity. This is the first paper to propose such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT. Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2020} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design. On the contrary, this paper focus on multi-carrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.

			\textit{Second}, we formulate an optimization for this joint waveform, active and passive beamforming design so as to characterize the R-E region achieved by the proposed architecture. The R-E region characterization problem is transformed into multiple energy maximization problems subject to rate constraints. Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS, 2) waveform and active beamforming at the transmitter and power splitting ratio at the receiver, until convergence. On top of the SWIPT optimization based on Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs an low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in a efficient and reliable manner. Though no rigorous mathematical proof exists for the convergence of the relaxed IRS phase shift problem, numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.

			\textit{Third}, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture. It is confirmed that the observations for SWIPT carries on to IRS-aided SWIPT. For example, dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, while TS and PS are preferred at low and high SNR, respectively. Results also confirmed that the IRS bring a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy. Different from the active amplify-and-forward (AF) relay with optimal location around the midpoint \cite{Li2017}, the passive IRS should be placed next to either the transmitter or the receiver, due to the product-distance path loss model. It implies that that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems. For active beamforming, increasing the number of transmit antennas brings a linear growth in SNR and a quadratic boost in harvested DC power. For passive beamforming, increasing the number of reflect elements provides a quadratic growth in SNR and a quartic boost in harvested DC power. Moreover, the adaptive IRS design outperforms the non-adaptive (rate/energy-optimized) ones for broadband transmission, while the performance of all three strategies coincides with the ideal Frequency-Selective (FS) IRS for narrowband transmission.

			\textit{Organization:} The rest of this paper is organized as follows. Section~\ref{se:system_model} introduces the signal, channel, receiver and R-E tradeoff models of the IRS-aided SWIPT system. Section~\ref{se:problem_formulation} tackles the waveform, active and passive beamforming optimization. Section~\ref{se:performance_evaluation} presents simulation results to evaluate the proposed design. Section~\ref{se:conclusion_and_future_works} concludes the paper.

@@

	\begin{section}{System Model}\label{se:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{\columnwidth}
			\import{assets/}{system.pdf_tex}
			\caption{An IRS-aided OFDM SWIPT system.}
			\label{fi:system}
		\end{figure}

		As shown in Fig.~\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands with center frequency $f_n$ ($n=1,\dots,N$). Perfect Channel State Information (CSI) at the transmitter, IRS and receiver with negligible training overhead are assumed to explore the upper bound of the proposed design. A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged. Two practical co-located receiver architectures are compared in terms of R-E region. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and beamforming design. Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by IRS for two and more times are omitted. We also assume the noise power is too small to be harvested.

@@

			By discarding the non-DC components, taking expectation over symbol distribution, and truncating \eqref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as

@@

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize the R-E region through a current maximization problem subject to transmit power, IRS magnitude, and rate constraints
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_I}\rVert^2+\lVert{\boldsymbol{w}_P}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1\,.}
		\end{maxi!}
		Problem~\eqref{op:original} is intricate as the variables are coupled and the objective function \eqref{ob:original}, the rate constraint \eqref{co:original_rate}, and the IRS magnitude constraint \eqref{co:original_modulus} are non-convex. To achieve a feasible solution, we propose a AO algorithm that iteratively updates the waveform and active beamforming at the transmitter, the phase shift at the IRS, and the power splitting ratio at the receiver, until convergence.
		\begin{remark}\label{re:irs_subchannel_alignment}
			As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of IRS introduces a resource allocation problem. Following Remark \ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflector can simultaneously align the corresponding AP-IRS-user channel with the AP-user channel at all subbands. In this case, the strength of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
		\end{remark}

@@

			That is to say, for single-user MISO SWIPT, the optimal active beamformer is MRT and we only need to determine the amplitudes $s_{I/P,n}$ at different tones. Hence, the original waveform optimization with $2MN$ complex variables is converted into a power allocation problem with $2N$ nonnegative real variables. Let $\boldsymbol{s}_{I/P}=[s_{I/P,1},\dots,s_{I/P,N}]^T \in \mathbb{C}^{N \times 1}$. At subband $n$, the effective channel gain is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{I,n}^2$ and $s_{P,n}^2$, respectively. With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective function further reduces to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, respectively.

@@

		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \textit{First}, it is observed that increasing $N$ reduces the average per-subband rate $R/N$ but boosts the harvested energy. The reason is that the power budget is divided into smaller portions for each subband, but more balanced terms $m_P$ are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}. Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference between modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain. Therefore, superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4). \textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e. a time sharing between the WPT point and the tangent WIPT point obtained by PS. Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favouring a different waveform and transceiving strategy, both heavily depends on $N$.

>>>>

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the transmission efficiency by providing a passive beamforming gain. This paper investigates an IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS. Considering the rectifier nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user. Stationary solutions are achieved based on Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by Geometric Programming (GP) technique. It is confirmed that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH), such that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR). Simulation results also show that the IRS significantly enlarges the R-E region while preserving the waveform preference and transceiving strategy. Although the AP-IRS-user extra link is relatively weak, we found that the information and power benefits of passive beamforming scale much faster than those of active beamforming. It suggests using more active antennas for small-scale SWIPT and more passive elements for large-scale SWIPT. % The proposed design enables a joint control of transmitter, receiver and wireless channel.
	\end{abstract}

@@

			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the rectifier input power level and input waveform shape. It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then designed joint waveform and beamforming design for WPT. Simulation and experiments demonstrated that ignoring the energy harvester nonlinearity is inaccurate and emphasized the benefit of modeling such nonlinearity in real system design \cite{Kim2019,Kim2020a}. Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand the operation range. Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}. Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of PS and TS is generally the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?". This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g. modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
		\end{subsection}

@@

			Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at a specific frequency to mitigate signal attenuation. Motivated by this, \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Wu2019}. Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting. In \cite{Nadeem2019}, channel estimation for Time-Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each reflector with the others switched off. To reduce estimation overhead and design complexity, \cite{Yang2019} exploited the spatial correlation and proposed a group-based IRS model where adjacent elements share a common reflection coefficient. Recent research also explored the possibility of integrating IRS into Orthogonal Frequency-Division Multiplexing (OFDM) systems. For example, \cite{Yang2020} further enhances time diversity by dynamic passive beamforming that varies IRS over consequent time slots, to enable flexible resource allocation over time-frequency Resource Blocks (RBs). In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time high-definition video transmission at \si{GHz} and mmWave frequency.
		\end{subsection}

		\begin{subsection}{IRS-Aided SWIPT}
			The effective channel enhancement and low power consumption of the IRS are expected to bring more opportunities to SWIPT. It was argued in \cite{Wu2020b} that a dedicated energy beam is power-inefficient and may cause interference, thus not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system. On the other hand, \cite{Tang2019} suggested that if the interference can be canceled, multiple energy beams are generally required for the max-min harvested power problem. \cite{Wu2020a} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update the transmit precoder and the IRS phase shifts, while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated. In such cases, a single energy stream is enough for all energy receivers. However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission and consider an inaccurate and oversimplified linear energy harvester model.

			In this paper, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of the IRS. The contributions of the paper are listed as follows.

			\textit{First}, we introduce a novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design. This architecture can be seen to IRS-aided SWIPT what \cite{Clerckx2018b} is to SWIPT. Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user. A multi-carrier unmodulated power waveform (deterministic multisine) is superposed to a multi-carrier modulated information waveform to boost the energy transfer efficiency. The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS, and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity. This is the first paper to propose such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT. Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2020} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design. On the contrary, this paper focuses on multi-carrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.

			\textit{Second}, we formulate an optimization for this joint waveform, active and passive beamforming design to characterize the R-E region achieved by the proposed architecture. The R-E region characterization problem is transformed into multiple energy maximization problems subject to rate constraints. Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS, 2) waveform, active beamforming at the transmitter and power splitting ratio at the receiver, until convergence. On top of the SWIPT optimization based on Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs a low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in an efficient and reliable manner. Though no rigorous mathematical proof exists for the convergence of the relaxed IRS phase shift problem, numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.

			\textit{Third}, we conduct numerical evaluations that demonstrate the benefit of the proposed architecture. It is confirmed that the observations for SWIPT carry on to IRS-aided SWIPT. For example, a dedicated power waveform can boost the energy transmission efficiency for multi-carrier transmission, while TS and PS are preferred at low and high SNR, respectively. Results also confirmed that the IRS brings a significant channel amplification and R-E enhancement with no impact on the waveform preference and transceiving strategy. Different from the active amplify-and-forward (AF) relay with optimal location around the midpoint \cite{Li2017}, the passive IRS should be placed next to either the transmitter or the receiver due to the product-distance path loss model. It implies that equipping the AP with an IRS can effectively extend the operation range of SWIPT systems. For active beamforming, increasing the number of transmit antennas brings a linear growth in SNR and a quadratic boost in harvested DC power. For passive beamforming, increasing the number of reflect elements provides a quadratic growth in SNR and a quartic boost in harvested DC power. Moreover, the adaptive IRS design outperforms the non-adaptive (rate/energy-optimized) ones for broadband transmission, while the performance of all three strategies coincides with the ideal Frequency-Selective (FS) IRS for narrowband transmission.

			\textit{Organization:} The rest of this paper is organized as follows. Section~\ref{se:system_model} introduces the signal, channel, receiver, and R-E tradeoff models of the IRS-aided SWIPT system. Section~\ref{se:problem_formulation} tackles the waveform, active and passive beamforming optimization. Section~\ref{se:performance_evaluation} presents simulation results to evaluate the proposed design. Section~\ref{se:conclusion_and_future_works} concludes the paper.

@@

	\begin{section}{System Model}\label{se:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{\columnwidth}
			\import{assets/}{system.pdf_tex}
			\caption{An IRS-aided multi-carrier SWIPT system.}
			\label{fi:system}
		\end{figure}

		As shown in Fig.~\ref{fi:system}, we consider an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-reflector IRS, to a single-antenna user over $N$ orthogonal evenly-spaced subbands with center frequency $f_n$ ($n=1,\dots,N$). Perfect Channel State Information (CSI) at the transmitter, IRS and receiver with negligible training overhead are assumed to explore the upper bound of the proposed design. A quasi-static block fading channel model is considered for all links, and we focus on one particular block where the channels are approximately unchanged. Two practical co-located receiver architectures are compared in terms of the R-E region. Specifically, TS divides each time slot into orthogonal data and energy slots and performs a time sharing between WPT and Wireless Information Transfer (WIT). In comparison, PS splits the received signal into individual ID and EH streams such that the splitting ratio $\rho$ is coupled with waveform and beamforming design. Perfect synchronization is assumed among the three parties in both scenarios, and signals reflected by the IRS for two and more times are omitted. We also assume the noise power is too small to be harvested.

@@

			By discarding the non-DC components, taking an expectation over symbol distribution, and truncating \eqref{eq:i_d} to the $n_0$-th order, we approximate the average output DC current for a given channel as

@@

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize the R-E region through a current maximization problem subject to transmit power, IRS magnitude, and rate constraints
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_I,\boldsymbol{w}_P,\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_I}\rVert^2+\lVert{\boldsymbol{w}_P}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1\,.}
		\end{maxi!}
		Problem~\eqref{op:original} is intricate as the variables are coupled and the objective function \eqref{ob:original}, the rate constraint \eqref{co:original_rate}, and the IRS magnitude constraint \eqref{co:original_modulus} are non-convex. To achieve a feasible solution, we propose an AO algorithm that iteratively updates the waveform and active beamforming at the transmitter, the phase shifts at the IRS, and the power splitting ratio at the receiver, until convergence.
		\begin{remark}\label{re:irs_subchannel_alignment}
			As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of the IRS introduces a resource allocation problem. Following Remark \ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflector can simultaneously align the corresponding AP-IRS-user channel with the AP-user channel at all subbands. In this case, the strengths of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
		\end{remark}

@@

			That is to say, for single-user MISO SWIPT, the optimal active beamformer is MRT and we only need to determine the amplitudes $s_{I/P,n}$ at different tones. Hence, the original waveform optimization with $2MN$ complex variables is converted into a power allocation problem with $2N$ nonnegative real variables. Let $\boldsymbol{s}_{I/P}=[s_{I/P,1},\dots,s_{I/P,N}]^T \in \mathbb{C}^{N \times 1}$. At subband $n$, the effective channel gain is given by $\lVert{\boldsymbol{h}_n}\rVert$, and the power allocated to the modulated and unmodulated waveform are given by $s_{I,n}^2$ and $s_{P,n}^2$, respectively. With such an active beamformer selection, we have $\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}=\lvert{\boldsymbol{h}_n^H\boldsymbol{w}_{I,n}}\rvert=\lVert{\boldsymbol{h}_n}\rVert s_{I,n}$ such that the rate and objective functions further reduce to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, respectively.

@@

		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \textit{First}, it is observed that increasing $N$ reduces the average per-subband rate $R/N$ but boosts the harvested energy. The reason is that the power budget is divided into smaller portions for each subband, but more balanced terms $m_P$ are introduced to further amplify the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}. Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that from the perspective of WPT, a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference between modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathcal{E}\left\{\mathcal{A}\left\{y_{I}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathcal{A}\left\{y_{P}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gain. Therefore, the superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4). \textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e. a time sharing between the WPT point and the tangent WIPT point obtained by PS. Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving strategy, both heavily depends on $N$.
